On exponential sums arising from the doubling method

### 2024-12-12 paper.tex
Defining gamma factors

\newcommand{\parabolicSection}{\Phi^{\left(z_1, \dots, z_c\right)}}
\newcommand{\intertwiningOperator}{M^{\left(z_1, \dots, z_c\right)}}
\newcommand{\holomorphicRepresentation}{\depthZeroRepresentation^{\left(z_1, \dots, z_c\right)}}
\newcommand{\WhittakerFunctional}[1]{\ell_{#1, \fieldCharacter}}
\newcommand{\gWhittakerFunctional}[2]{\ell_{#1, #2}}
\newcommand{\gSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}, \fieldCharacter_{\UnipotentRadicalForWss{#2}{#3}}}}
\newcommand{\gShortSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}}}
\newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
\newcommand{\dblGaussSum}[2]{\mathcal{G}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblGaussSumScalar}[2]{\mathrm{G}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\GKGaussSum}[3]{\mathcal{G}\left(#1 \times #2, #3\right)}
\newcommand{\GKGaussSumScalar}[3]{\mathrm{G}\left(#1 \times #2, #3\right)}
\newcommand{\fieldCharacterkc}[2]{\fieldCharacter_{\left({#2}^{#1}\right)}}
\newcommand{\ExoticKloosterman}{\mathrm{Kl}}
\newcommand{\GaussSumCharacter}[4]{\tau_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\IrrCusp}{\Irr_{\mathrm{cusp}}}
\newcommand{\convolutionWithCompactSupport}{\boldsymbol{\mathrm{R}}}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\artinScrier}{\operatorname{AS}}
\newcommand{\KloostermanSumClassFunction}{\mathcal{K}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}

@@

Consider the following assignment $\GL_n\left(\finiteField\right) \to \cComplex$
$$\Phi_{\chi}\left(g\right) = \begin{dcases}
	\chi\left(\det\left(g-\IdentityMatrix{n}\right)\right) & \text{if }\det\left(g-\IdentityMatrix{n}\right) \ne 0,\\
	0 & \text{otherwise.}
\end{dcases}$$
It is clear that $\Phi_{\chi}$ is a class function of $\GL_n\left(\finiteField\right)$. Given an irreducible representation $\tau$ of $\GL_n\left(\finiteField\right)$, we consider the following \emph{doubling method Gauss sum}:
$$\dblGaussSum{\tau}{\chi} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
Then $\dblGaussSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$. Therefore, by Schur's lemma there exists a complex number $\dblGaussSumScalar{\tau}{\chi} \in \cComplex$ such that $$\dblGaussSum{\tau}{\chi} = \dblGaussSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$

@@

Assume first that $1$ does not appear in the cuspidal support of $\tau$. Let us write
$$\dblGaussSum{\tau}{\chi} = q^{-\frac{n^2}{2}} \sum_{\substack{g \in \GL_n\left(\finiteField\right) \\
		\det\left(g - \IdentityMatrix{n}\right) \ne 0}} \chi\left(\det\left(g - \IdentityMatrix{n}\right)\right) \tau\left(g\right).$$
We rewrite this using a Fourier transform type expression
$$\dblGaussSum{\tau}{\chi} = q^{-\frac{3n^2}{2}} \sum_{g, h \in \GL_n\left(\finiteField\right)} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(g\right) \fieldCharacter\left(\trace\left(A \left(\IdentityMatrix{n} - h \left(g - \IdentityMatrix{n}\right)\right)\right)\right).$$

Replacing $g$ with $h^{-1} g$, we arrive at the expression
\begin{align*}
	\dblGaussSum{\tau}{\chi} =& q^{-\frac{3n^2}{2}} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \fieldCharacter\left(\trace A\right) \sum_{h \in \GL_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(h^{-1}\right) \fieldCharacter\left(\trace\left(Ah\right)\right)\\
	& \circ \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \fieldCharacter\left(-\trace Ag\right).
\end{align*}
Since the last inner sum is $q^{\frac{n^2}{2}} \GaussSum{\tau}{\fieldCharacter}_{-A}$, we have that the sum can be reduced to $A \in \GL_n\left(\finiteField\right)$. Replacing $h$ with $A^{-1} h$ and $g$ with $-A^{-1} g$, we get the sum
\begin{align*}
	\dblGaussSumScalar{\tau}{\chi} &= q^{-\frac{n^2}{2}} \centralCharacter{\tau}\left(-1\right) \sum_{A \in \GL_n\left(\finiteField\right)} \chi\left(\det A\right) \fieldCharacter\left(\trace A\right) \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter},
\end{align*}
which equals
\begin{align*}
	\dblGaussSumScalar{\tau}{\chi} &=  \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^n \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter}.
\end{align*}
This is probably also true if $1$ is in the cuspidal support of $\tau$  and $\chi \ne 1$ (return to this later: should follow from a multiplicativity arguments). In the meantime, we will check this for $\tau = 1$, the trivial representation of $\GL_1\left(\finiteField\right)$, in which case we have
$$\dblGaussSum{1}{\chi} = q^{-\frac{1}{2}} \sum_{\substack{x \in \multiplicativegroup{\finiteField} \\
		x \ne 1}} \chi\left(x - 1\right) = q^{-\frac{1}{2}}\left(-\chi\left(-1\right) + \sum_{x \in \multiplicativegroup{\finiteField}} \chi\left(x\right) \right) = \begin{dcases}
		-q^{-\frac{1}{2}} \chi\left(-1\right) & \chi \ne 1\\
		q^{-\frac{1}{2}} \left(q - 2\right) & \chi = 1
	\end{dcases}.$$

@@

\begin{theorem}
	Let $\pi'$ be an irreducible representation of $G'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\finiteField\right)$. Then for any irreducible representation $\pi$ of $G$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{G}{\tau \overline{\otimes} \pi'}$ and any $\chi \ne 1$, we have
	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \chi\left(-1\right)^k \GaussSumScalar{\chi^2}{\fieldCharacter}^k \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
\end{theorem}
\begin{proof}
	Let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$. Consider $f \in \rho$ defined as follows. The function $f \in \rho$ is the unique element supported on $P$, such that $f\left(\idmap_{\hermitianSpace}\right) = v_{\tau} \otimes v_{\pi'}$. The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero. We compute $\dblGaussSum{\pi}{\chi} f$.

@@

	Hence, we have that $\dblGaussSum{\pi}{\chi} f$ is supported on $P$. We move to compute $\left(\dblGaussSum{\pi}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P\\
				\det\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\det\left(p - \idmap_{\hermitianSpace}\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
	\end{equation}
	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\finiteField\right) \times G'$ then $$\det\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \det\left(a\right)^{-1}\det\left(a - I_k\right)^2 \det\left( g' - \idmap_{\hermitianSpace'}\right),$$
	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
	\begin{equation}
		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\finiteField\right)} \Phi_{\chi^2}\left(a\right) \chi^{-1}\left(\det a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
	\end{equation}
	which in turn is
	\begin{align*}
		&\chi\left(-1\right)^k  \dblGaussSum{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'} \\
		=& \chi\left(-1\right)^k \dblGaussSumScalar{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} \dblGaussSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
	\end{align*}
	The result now follows.
\end{proof}

@@

\begin{theorem}
	Suppose that $\pi$ is an irreducible cuspidal representation of $G$, parameterized by a character $\theta = \theta_1 \times \dots \times \theta_r$ of a torus $T$ isomorphic to $$T \cong \finiteFieldExtension{2n_1}^1 \times \finiteFieldExtension{2n_2}^1 \times \dots \finiteFieldExtension{2n_r}^1,$$
	where $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace$ if $\dim \hermitianSpace$ is even or $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace - 1$ if $\dim \hermitianSpace$ is odd, and where $$\finiteFieldExtension{2m}^1 = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
	Then up to some signs and some power of $\GaussSumScalar{\chi}{\fieldCharacter}$, we have $$\dblGaussSumScalar{\pi}{\chi}= \prod_{j=1}^r \tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j} \right),$$
	where $\theta'_j\left(x\right) = \theta_j\left(x^{1-q^{m_j}}\right)$ and $$\tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j}\right) = -\sum_{x \in \multiplicativegroup{\finiteFieldExtension{2n_j}}} \theta'_j\left(x\right) \chi\left(\FieldNorm{2n_j}{1}\left(x\right)\right)\fieldCharacter\left(\trace_{\finiteFieldExtension{2n_j} \slash \finiteField}\left(x\right)\right).$$
\end{theorem}

>>>>

\newcommand{\parabolicSection}{\Phi^{\left(z_1, \dots, z_c\right)}}
\newcommand{\intertwiningOperator}{M^{\left(z_1, \dots, z_c\right)}}
\newcommand{\holomorphicRepresentation}{\depthZeroRepresentation^{\left(z_1, \dots, z_c\right)}}
\newcommand{\WhittakerFunctional}[1]{\ell_{#1, \fieldCharacter}}
\newcommand{\gWhittakerFunctional}[2]{\ell_{#1, #2}}
\newcommand{\gSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}, \fieldCharacter_{\UnipotentRadicalForWss{#2}{#3}}}}
\newcommand{\gShortSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}}}
\newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
\newcommand{\dblGaussSum}[2]{\mathcal{G}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblGaussSumScalar}[2]{\mathrm{G}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\GKGaussSum}[3]{\mathcal{G}\left(#1 \times #2, #3\right)}
\newcommand{\GKGaussSumScalar}[3]{\mathrm{G}\left(#1 \times #2, #3\right)}
\newcommand{\fieldCharacterkc}[2]{\fieldCharacter_{\left({#2}^{#1}\right)}}
\newcommand{\ExoticKloosterman}{\mathrm{Kl}}
\newcommand{\GaussSumCharacter}[4]{\tau_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\IrrCusp}{\Irr_{\mathrm{cusp}}}
\newcommand{\convolutionWithCompactSupport}{\boldsymbol{\mathrm{R}}}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\artinScrier}{\operatorname{AS}}
\newcommand{\KloostermanSumClassFunction}{\mathcal{K}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}

@@

Consider the following assignment $\GL_k\left(\finiteField\right) \to \cComplex$
$$\Phi_{\chi}\left(g\right) = \begin{dcases}
	\chi\left(\det\left(g-\IdentityMatrix{k}\right)\right) & \text{if }\det\left(g-\IdentityMatrix{k}\right) \ne 0,\\
	0 & \text{otherwise.}
\end{dcases}$$
It is clear that $\Phi_{\chi}$ is a class function of $\GL_k\left(\finiteField\right)$. Given an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we consider the following \emph{doubling method Gauss sum}:
$$\dblGaussSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
Then $\dblGaussSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_k\left(\finiteField\right)}\left(\tau, \tau\right)$. Therefore, by Schur's lemma there exists a complex number $\dblGaussSumScalar{\tau}{\chi} \in \cComplex$ such that $$\dblGaussSum{\tau}{\chi} = \dblGaussSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$

@@

Assume first that $1$ does not appear in the cuspidal support of $\tau$. Let us write
$$\dblGaussSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{\substack{g \in \GL_k\left(\finiteField\right) \\
		\det\left(g - \IdentityMatrix{k}\right) \ne 0}} \chi\left(\det\left(g - \IdentityMatrix{k}\right)\right) \tau\left(g\right).$$
We rewrite this using a Fourier transform type expression
$$\dblGaussSum{\tau}{\chi} = q^{-\frac{3k^2}{2}} \sum_{g, h \in \GL_k\left(\finiteField\right)} \sum_{A \in \squareMatrix_k\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(g\right) \fieldCharacter\left(\trace\left(A \left(\IdentityMatrix{k} - h \left(g - \IdentityMatrix{k}\right)\right)\right)\right).$$

Replacing $g$ with $h^{-1} g$, we arrive at the expression
\begin{align*}
	\dblGaussSum{\tau}{\chi} =& q^{-\frac{3k^2}{2}} \sum_{A \in \squareMatrix_k\left(\finiteField\right)} \fieldCharacter\left(\trace A\right) \sum_{h \in \GL_k\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(h^{-1}\right) \fieldCharacter\left(\trace\left(Ah\right)\right)\\
	& \circ \sum_{g \in \GL_k\left(\finiteField\right)} \tau\left(g\right) \fieldCharacter\left(-\trace Ag\right).
\end{align*}
Since the last inner sum is $q^{\frac{k^2}{2}} \GaussSum{\tau}{\fieldCharacter}_{-A}$, we have that the sum can be reduced to $A \in \GL_k\left(\finiteField\right)$. Replacing $h$ with $A^{-1} h$ and $g$ with $-A^{-1} g$, we get the sum
\begin{align*}
	\dblGaussSumScalar{\tau}{\chi} &= q^{-\frac{k^2}{2}} \centralCharacter{\tau}\left(-1\right) \sum_{A \in \GL_k\left(\finiteField\right)} \chi\left(\det A\right) \fieldCharacter\left(\trace A\right) \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter},
\end{align*}
which equals
\begin{align*}
	\dblGaussSumScalar{\tau}{\chi} &=  \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter}.
\end{align*}
This is probably also true if $1$ is in the cuspidal support of $\tau$  and $\chi \ne 1$ (return to this later: should follow from a multiplicativity arguments). In the meantime, we will check this for $\tau = 1$, the trivial representation of $\GL_1\left(\finiteField\right)$, in which case we have
$$\dblGaussSum{1}{\chi} = q^{-\frac{1}{2}} \sum_{\substack{x \in \multiplicativegroup{\finiteField} \\
		x \ne 1}} \chi\left(x - 1\right) = q^{-\frac{1}{2}}\left(-\chi\left(-1\right) + \sum_{x \in \multiplicativegroup{\finiteField}} \chi\left(x\right) \right) = \begin{dcases}
		-q^{-\frac{1}{2}} \chi\left(-1\right) & \chi \ne 1\\
		q^{-\frac{1}{2}} \left(q - 2\right) & \chi = 1
	\end{dcases}.$$

@@

\begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
	Let $\pi'$ be an irreducible representation of $G'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\finiteField\right)$. Then for any irreducible representation $\pi$ of $G$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{G}{\tau \overline{\otimes} \pi'}$ and any $\chi \ne 1$, we have
	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^k \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
\end{theorem}
\begin{proof}
	Let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$. Consider $f \in \rho$ defined as follows. The function $f \in \rho$ is the unique element supported on $P$, such that $f\left(\idmap_{\hermitianSpace}\right) = v_{\tau} \otimes v_{\pi'}$. The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero. We compute $\dblGaussSum{\pi}{\chi} f$.

@@

	Hence, we have that $\dblGaussSum{\pi}{\chi} f$ is supported on $P$. We move to compute $\left(\dblGaussSum{\pi}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P\\
				\det\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\det\left(p - \idmap_{\hermitianSpace}\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
	\end{equation}
	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\finiteField\right) \times G'$ then $$\det\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \det\left(a\right)^{-1}\det\left(a - I_k\right)^2 \det\left( g' - \idmap_{\hermitianSpace'}\right),$$
	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
	\begin{equation}
		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\finiteField\right)} \Phi_{\chi^2}\left(a\right) \chi^{-1}\left(\det a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
	\end{equation}
	which in turn is
	\begin{align*}
		&\chi\left(-1\right)^k \dblGaussSum{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'}\\
		=& \chi\left(-1\right)^k\dblGaussSumScalar{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} \dblGaussSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
	\end{align*}
	The result now follows.
\end{proof}

\subsubsection{Gamma factors}
In order to make the computations more tolerable, it is beneficial to work with fully multiplicative functions. We introduce the doubling method gamma factors.

For an irreducible representation  $\tau$ of $\GL_k\left(\finiteField\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left[\frac{\dim \hermitianSpace}{2}\right]}}.$$
Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.

\begin{theorem}
	\begin{enumerate}
		\item If $\tau_1$ and $\tau_2$ are irreducible representations of $\GL_{k_1}\left(\finiteField\right)$ and $\GL_{k_2}\left(\finiteField\right)$, respectively, then for any irreducible subrepresentation $\tau$ of the parabolic induction $\tau_1 \circ \tau_2$, we have
		$$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \dblGammaFactor{\tau_1}{\chi}{\fieldCharacter} \dblGammaFactor{\tau_2}{\chi}{\fieldCharacter}.$$
		\item If $\tau$, $\pi'$ and $\pi$ are as in \Cref{thm:multiplicativity-in-terms-of-gauss-sums} and $\chi \ne 1$, then
		$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \dblGammaFactor{\tau}{\chi}{\fieldCharacter}.$$
	\end{enumerate}
\end{theorem}

@@

\begin{theorem}
	Suppose that $\pi$ is an irreducible cuspidal representation of $G$, parameterized by a character $\theta = \theta_1 \times \dots \times \theta_r$ of a torus $T$ such that $$T \cong \finiteFieldExtension{2n_1}^1 \times \finiteFieldExtension{2n_2}^1 \times \dots \times \finiteFieldExtension{2n_r}^1,$$
	where $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace$ if $\dim \hermitianSpace$ is even or $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace - 1$ if $\dim \hermitianSpace$ is odd, and where $$\finiteFieldExtension{2m}^1 = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
	Then up to maybe a sign, we have $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \prod_{j=1}^r \tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j} \right),$$
	where $\theta'_j\left(x\right) = \theta_j\left(x^{1-q^{n_j}}\right)$ and $$\tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j}\right) = -q^{-n_j} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2n_j}}} \theta'_j\left(x\right) \chi\left(\FieldNorm{2n_j}{1}\left(x\right)\right)\fieldCharacter\left(\trace_{\finiteFieldExtension{2n_j} \slash \finiteField}\left(x\right)\right).$$
\end{theorem}
